\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\hypersetup{colorlinks=true, urlcolor=blue}

\begin{document}

\begin{center}
\textbf{Alberto Hern\'andez Espinosa} \\
Mexico City, Mexico $\bullet$ +52 552 383 4438 $\bullet$ albertohernandezespinosa@gmail.com \\
\url{linkedin.com/in/alberto-hernandeze} $\bullet$ \url{github.com/albertoHdzE}
\end{center}

\section{Professional Summary}
\begin{itemize}
\item 10+ years leading AI research and software development for universities and industry.
\item Expert in ML, deep learning, and causal AI, with proven impact (e.g., 53\% cloud cost reduction).
\item Published with Oxford University and Oxford Immune Algorithmics on AI and complexity.
\item 7+ years of global remote collaboration; adept with interdisciplinary AI teams.
\item AI Engineer Lead at K-Square Group, driving AI innovation.
\end{itemize}

\section{Skills \& Expertise}
\begin{itemize}
\item AI/ML: Python, TensorFlow, PyTorch, Scikit-learn, Keras, LangGraph, Ollama, RAG, Agents
\item Languages: Python, R, C++, SQL, Mathematica, FastAPI, React
\item Cloud/DevOps: GCP, AWS, Docker
\item Data Science: Big Data, SQL/NoSQL, ETL, Pandas, NumPy
\item Domains: AI, Complexity Science, Cognitive Science, Reinforcement Learning
\end{itemize}

\section{Professional Experience}
\subsection{AI Engineer Lead, K-Square Group (Remote)}
Nov 2024--Present
\begin{itemize}
\item Lead AI project teams, enhancing collaboration and execution.
\item Drive R\&D of AI/ML solutions for industry-specific challenges.
\item Oversee integration of advanced AI technologies and pipelines.
\item Develop strategic frameworks for rapid prototyping.
\item Mentor teams in AI tool utilization and innovation.
\end{itemize}

\subsection{Chief AI Scientist, MilkStraw AI, San Francisco, CA (Remote)}
Oct 2022--Sep 2024
\begin{itemize}
\item Led AI-driven cloud optimization on AWS, saving 53\% costs.
\item Designed ML pipelines with Python, TensorFlow, PyTorch.
\item Collaborated globally on scalable AI solutions.
\end{itemize}

\subsection{Research Director, Laxford Capital (Remote)}
Jun 2019--Jul 2022
\begin{itemize}
\item Directed AI trading with reinforcement learning agents.
\item Oversaw model design in Python and PyTorch.
\item Improved trading via causal AI approaches.
\end{itemize}

\subsection{Research Collaborator, Oxford Immune Algorithmics \& Oxford University (Remote)}
2015--Nov 2024
\begin{itemize}
\item Contributed to AI and complexity publications.
\item Implemented models in Mathematica and Python.
\item Co-authored with Oxford researchers.
\end{itemize}

\section{Education}
\subsection{PhD in Philosophy of Science, UNAM, Mexico City}
2015--2019 (Specialization: AI and Cognitive Science)
\begin{itemize}
\item Focused on integrated information theory.
\item CONACyT Scholarship, collaborated with Oxford.
\end{itemize}

\subsection{Master in Computer Sciences, UNAM, Mexico City}
2012--2014 (Specialization: AI)
\begin{itemize}
\item Thesis on computational creativity.
\item CONACyT Scholarship.
\end{itemize}

\section{Selected Projects}
\begin{itemize}
\item Noesis: AI/ML platform for regression, classification, clustering (GitHub: \url{https://github.com/KSProjectX/test-xx}, restricted).
\item KS-Onboarding: Agentic project control with OCR and RAG (GitHub: \url{https://github.com/KSProjectX/KS-onboarding}, restricted; arXiv: \url{https://arxiv.org/abs/2505.02581}).
\item Test Automation Agents: Dynamic pytest generation (GitHub: \url{https://github.com/Sucharita8/KS-qe-platform}, restricted).
\item Stock Prices Prediction: RL and ML for forecasting (GitHub: \url{https://github.com/albertoHdzE/finance_1}).
\item Tononi's Phi: Consciousness measure in Mathematica (GitHub: \url{https://github.com/albertoHdzE/Alpha}).
\item MOSAICA: DNA complexity analysis (GitHub: \url{https://github.com/albertoHdzE/MOSAICA}).
\end{itemize}

\section{Publications}
\begin{itemize}
\item 2025: \url{https://arxiv.org/abs/2505.02581}
\item 2025: \url{https://arxiv.org/abs/2503.16743}
\item 2021: \url{https://www.worldscientific.com/doi/10.1142/9789811235726_0005}
\item 2017: \url{https://link.springer.com/chapter/10.1007/978-3-319-58741-7_2}
\item 2013: \url{https://link.springer.com/chapter/10.1007/978-3-642-37225-4_14}
\end{itemize}

\section{Certifications}
\begin{itemize}
\item Mathematics for Machine Learning
\item AI for Finance
\item Google Cloud Specialization
\end{itemize}
Full list of 47 certifications: \url{https://www.linkedin.com/in/alberto-hernandeze/details/certifications/}

\section{Languages}
\begin{itemize}
\item Spanish (mother language)
\item English (advanced)
\item German (Basic)
\item French (Basic)
\item Japanese (Basic)
\end{itemize}
Details: \url{https://www.linkedin.com/in/alberto-hernandeze/details/languages/}

\end{document}